Approximate State Abstraction

### 2015-12-10 paper/approximate_state_abstraction.tex
adding icml author kit

\documentclass[11pt]{article}
\usepackage{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\usepackage{aaai}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\title{Approximate State Abstraction}
\author{David Abel, D. Ellis Hershkowitz, Michael Littman}
\date{}                                           % Activate to display a given date or no date

@@

\begin{document}
\maketitle

@@

>>>>

\documentclass{article}
\usepackage{times}
\usepackage{graphicx}
\usepackage{subfigure} 
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}} % Fixes misbehavior of conflicting packages.
\usepackage{icml2016/icml2016}

\icmltitlerunning{Approximate State Abstraction}

@@

% --- DOCUMENT ---
\begin{document}

\twocolumn[
\icmltitle{Approximate State Abstraction}

% Paper Meta Info
\icmlauthor{David Abel}{david_abel@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}
\icmlauthor{D. Ellis Hershkowitz}{david_hershkowitz@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}
\icmlauthor{Michael Littman}{michael_littman@brown.edu}
\icmladdress{Brown University,
            115 Waterman Street, Providence, RI 02906}

\icmlkeywords{Reinforcement Learning, State Aggregation, State Abstraction, Planning, MDP}

\vskip 0.3in
]

@@

% Set of actions within epsilon (Q*) is the same for two states? Better than boltzmann.
